Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
Section titles
rewrite intro

%Current state of affairs 
Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}. These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}). GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}. 
%Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations. In such scenarios such as in many reinforcement learning environments neural networks are used as the surrogate model. However, uncertainty is still essential to ensure effective exploration for sequential algorithms. Successful approaches have attempted to blend neural networks with uncertainty estimates around predictions, allowing for sophisticated exploration strategies. However, there has been limited use of hybrid models that possess the feature representation ability of neural networks but also attractive the properties of GPs, such a hybrid method we propose in this paper.

>>>>

%Current state of affairs 
Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}. These methods rely on the linearization of neural networks. \cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}). GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}. 
%Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations. In such scenarios such as in many reinforcement learning environments neural networks are used as the surrogate model. However, uncertainty is still essential to ensure effective exploration for sequential algorithms. Successful approaches have attempted to blend neural networks with uncertainty estimates around predictions, allowing for sophisticated exploration strategies. However, there has been limited use of hybrid models that possess the feature representation ability of neural networks but also attractive the properties of GPs, such a hybrid method we propose in this paper.
